The Unicode Cookbook \linebreak for Linguists

### 2018-06-11 book/langsci/seriesinfo/cfls-info.tex
migrate to newer class

\textbf{Series editors}\\
Mark Dingemanse \textit{Max Planck Institute for Psycholinguistics}   \\
Nick J. Enfield \textit{University of Sydney}

@@

\textbf{Editorial board} \\
Balthasar Bickel \textit{University of Zürich}   \\
Claire Bowern \textit{Yale University}          \\
Elizabeth Couper-Kuhlen \textit{University of Helsinki}    \\
William Croft \textit{University of New Mexico}            \\
Rose-Marie Déchaine \textit{University of British Columbia}      \\
William A. Foley \textit{University of Sydney}                   \\
William F. Hanks \textit{University of California at Berkeley}   \\
Paul Kockelman \textit{Yale University}           \\
Keren Rice \textit{University of Toronto}         \\
Sharon Rose \textit{University of California at San Diego }       \\
Frederick J. Newmeyer \textit{University of Washington}        \\
Wendy Sandler \textit{University of Haifa }            \\
Dan Sperber \textit{Jean Nicod Institute}     \\

@@

No scientific work proceeds without conceptual foundations. In language science, our concepts about language determine our assumptions, direct our attention, and guide our hypotheses and our reasoning. Only with clarity about conceptual foundations can we pose coherent research questions, design critical experiments, and collect crucial data.

\medskip

This series publishes short and accessible books that explore well-defined topics in the conceptual foundations of language science. The series provides a venue for conceptual arguments and explorations that do not require the traditional book-length treatment, yet that demand more space than a typical journal article allows.  
\end{minipage}

@@

\begin{enumerate}
\item Nick J. Enfield. \textit{Natural Causes of Language}.

@@

% 
% \vfill
% 
% \gdef\lsISSN{2363-5568}%
% \hfill ISSN: \lsISSN

>>>>

\textbf{Series editors}\\
Mark Dingemanse, \textit{Max Planck Institute for Psycholinguistics}   \\
N. J. Enfield, \textit{University of Sydney}

@@

\textbf{Editorial board}\\
Balthasar Bickel, \textit{University of Zürich},
Claire Bowern, \textit{Yale University},
Elizabeth Couper-Kuhlen, \textit{University of Helsinki},
William Croft, \textit{University of New Mexico},
Rose-Marie Déchaine, \textit{University of British Columbia},
William A. Foley, \textit{University of Sydney} ,
William F. Hanks, \textit{University of California at Berkeley},
Paul Kockelman, \textit{Yale University},
Keren Rice, \textit{University of Toronto},
Sharon Rose, \textit{University of California at San Diego},
Frederick J. Newmeyer, \textit{University of Washington},
Wendy Sandler, \textit{University of Haifa},
Dan Sperber \textit{Central European University}

\bigskip
\bigskip

@@

No scientific work proceeds without conceptual foundations. In language science, our concepts about language determine our assumptions, direct our attention, and guide our hypotheses and our reasoning. Only with clarity about conceptual foundations can we pose coherent research questions, design critical experiments, and collect crucial data.
%
This series publishes short and accessible books that explore well-defined topics in the conceptual foundations of language science. The series provides a venue for conceptual arguments and explorations that do not require the traditional book-length treatment, yet that demand more space than a typical journal article allows.
\end{minipage}

\bigskip
\bigskip

@@

\begin{enumerate}
\item N. J. Enfield. \textit{Natural causes of language}.

@@

### 2018-06-11 book/langsci/seriesinfo/silp-info.tex
migrate to newer class

{\raggedleft\IfFileExists{./LSP/lsp-seriesinfo/labphon-logo.pdf}{\includegraphics[width=5cm]{./LSP/lsp-seriesinfo/labphon-logo.pdf}}{LabPhon-Logo}}

@@

\begin{enumerate}
\item Cangemi, Francesco. Prosodic detail in Neapolitan Italian
\end{enumerate}

\vfill

\gdef\lsISSN{2363-5576}%
\hfill ISSN: \lsISSN

>>>>

{\raggedleft\IfFileExists{./langsci/seriesinfo/labphon-logo.pdf}{\includegraphics[width=5cm]{./langsci/seriesinfo/labphon-logo.pdf}}{LabPhon-Logo}}

@@

\begin{enumerate}
\item Cangemi, Francesco. Prosodic detail in Neapolitan Italian.
\item Drager, Katie. linguistic variation, identity construction, and cognition.
\end{enumerate}
